Model LF

### 2023-03-11 paper version 2.Rmd
Commit

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur
s_g_bs1 = Shock_bs1$simulation$s_g
yh_g_bs1 = Shock_bs1$simulation$yh_g
i_g_bs1 = Shock_bs1$simulation$i_g
ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk
yd_g_bs1 = Shock_bs1$simulation$yd_g
tax_g_bs1 = Shock_bs1$simulation$tax_g
w_h_r_bs1 = Shock_bs1$simulation$w_h_r
tax_h_bs1 = Shock_bs1$simulation$tax_h
tax_g
nben_g_bs1 = Shock_bs1$simulation$nben_g
ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1

c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_bs2 = Shock_bs2$simulation$yk
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
nben_h_un_bs2 = Shock_bs2$simulation$nben_h_un
ur_bs2 = Shock_bs2$simulation$ur
net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

ik_bs2 = Shock_bs2$simulation$ik
mk_bs2 = Shock_bs2$simulation$mk

@@

c_ratio_bs2 = pconk_ds_bs2/yk_ds_bs2
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_bs3 = Shock_bs3$simulation$yk
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un
prodk_bs3 = Shock_bs3$simulation$prodk
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
lf_bs3 = Shock_bs3$simulation$lf
nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation
y_bs3 = Shock_bs3$simulation$y
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock
s_g_bs3 = Shock_bs3$simulation$s_g
i_g_bs3 = Shock_bs3$simulation$i_g
yd_g_bs3 = Shock_bs3$simulation$yd_g
ur_bs3 = Shock_bs3$simulation$ur
nben_g_bs3 = Shock_bs3$simulation$nben_g
nsben_h_bs3 = Shock_bs3$simulation$nsben_h
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_bs4 = Shock_bs4$simulation$yk
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
lf_bs4 = Shock_bs4$simulation$lf
tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio
ur_bs4 = Shock_bs4$simulation$ur
nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
s_h_bs4 = Shock_bs4$simulation$s_h
inflation_bs4 = Shock_bs4$simulation$inflation
y_bs4 = Shock_bs4$simulation$y
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
prod_ds_bs4 = Shock_bs4$simulation$prod_ds
prod_ds_shock_bs4 = Shock_bs4$simulation$prod_ds_shock

ur_bs4 = Shock_bs4$simulation$ur
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
w_h_r
```

```{r, fig.width=8, fig.height=8}
par(mfrow=c(2,2))

plot(yd_g_01-yd_g_bs1, col= "red")
plot(tax_g_01-tax_g_bs1, col= "red")
plot(tax_h_01-tax_h_bs1, col= "red")
plot(nben_g_01 -nben_g_bs1, col= "red")

plot(nben_h_un_01 - nben_h_un_bs1, col= "red")

plot(w_h_r_01 - w_h_r_bs1, col= "red")
```

```{r, fig.width=8, fig.height=6}

plot((s_g_01- s_g_bs1), col= "red")

plot(yd_g_01-yd_g_bs1, col= "red")
plot(yh_g_01-yh_g_bs1, col= "red")
plot(tax_g_01-tax_g_bs1, col= "red")
plot(nben_g_01 - nben_g_bs1, col= "red")

plot(nben_h_un_01 - nben_h_un_bs1, col= "red")
```

@@

nben_h_un_02 = Shock_2$simulation$nben_h_un
yk_02 = Shock_2$simulation$yk
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
ur_02 = Shock_2$simulation$ur
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
unemp_sb_low = sens_1_base_low$simulation$unemp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

@@

 sens1_low = TIMESERIES(sens1_low+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

>>>>

```{r}
###Gengivelse af stød til model
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_bs1 = Shock_bs1$simulation$yk
y_bs1 = Shock_bs1$simulation$y
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds
max_dp_bs1 = Shock_bs1$simulation$max_dp
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
xk_ds_bs1 = Shock_bs1$simulation$xk_ds
mk_ds_bs1 = Shock_bs1$simulation$mk_ds
lf_bs1 = Shock_bs1$simulation$lf
net_balance_bs1 = xk_ds_bs1 - mk_ds_bs1
net_balance_bs1_ratio= (xk_ds_bs1 - mk_ds_bs1)/yk_ds_bs1
nben_h_un_bs1 = Shock_bs1$simulation$nben_h_un
ur_bs1 = Shock_bs1$simulation$ur
s_g_bs1 = Shock_bs1$simulation$s_g
yh_g_bs1 = Shock_bs1$simulation$yh_g
i_g_bs1 = Shock_bs1$simulation$i_g
ik_bs1 = Shock_bs1$simulation$ik
mk_bs1 = Shock_bs1$simulation$mk
yd_g_bs1 = Shock_bs1$simulation$yd_g
tax_g_bs1 = Shock_bs1$simulation$tax_g
w_h_r_bs1 = Shock_bs1$simulation$w_h_r
tax_h_bs1 = Shock_bs1$simulation$tax_h
nben_g_bs1 = Shock_bs1$simulation$nben_g
ik_ratio_bs1 = ik_bs1/yk_ds_bs1
mk_ratio_bs1 = mk_bs1/yk_ds_bs1
c_ratio_bs1 = pconk_ds_bs1/yk_ds_bs1
gk_bs1 = Shock_bs1$simulation$gk

######### Hamid variable

AD_bs1= pconk_ds_bs1 + ik_bs1 + gk_bs1
TB_bs1= xk_ds_bs1 - mk_ds_bs1
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_bs2 = Shock_bs2$simulation$yk
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
nben_h_un_bs2 = Shock_bs2$simulation$nben_h_un
ur_bs2 = Shock_bs2$simulation$ur
net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2
gk_bs2 = Shock_bs2$simulation$gk
ik_bs2 = Shock_bs2$simulation$ik
mk_bs2 = Shock_bs2$simulation$mk

@@

c_ratio_bs2 = pconk_ds_bs2/yk_ds_bs2

######### Hamid variable

AD_bs2= pconk_ds_bs2 + ik_bs2 + gk_bs2
TB_bs2= xk_ds_bs2 - mk_ds_bs2
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_bs3 = Shock_bs3$simulation$yk
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
nben_h_un_bs3 = Shock_bs3$simulation$nben_h_un
prodk_bs3 = Shock_bs3$simulation$prodk
tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio
lf_bs3 = Shock_bs3$simulation$lf
nl_g_bs3 = Shock_bs3$simulation$nl_g
unemp_bs3 = Shock_bs3$simulation$unemp
s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation
y_bs3 = Shock_bs3$simulation$y
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
prod_ds_bs3 = Shock_bs3$simulation$prod_ds
prod_ds_shock_bs3 = Shock_bs3$simulation$prod_ds_shock
s_g_bs3 = Shock_bs3$simulation$s_g
i_g_bs3 = Shock_bs3$simulation$i_g
yd_g_bs3 = Shock_bs3$simulation$yd_g
ur_bs3 = Shock_bs3$simulation$ur
nben_g_bs3 = Shock_bs3$simulation$nben_g
nsben_h_bs3 = Shock_bs3$simulation$nsben_h
pconk_ds_bs3 = Shock_bs3$simulation$pconk_ds
ik_bs3 = Shock_bs3$simulation$ik
gk_bs3 = Shock_bs3$simulation$gk
xk_ds_bs3 = Shock_bs3$simulation$xk_ds
mk_ds_bs3 = Shock_bs3$simulation$mk_ds

######### Hamid variable

AD_bs3= pconk_ds_bs3 + ik_bs3 + gk_bs3
TB_bs3= xk_ds_bs3 - mk_ds_bs3
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_bs4 = Shock_bs4$simulation$yk
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
lf_bs4 = Shock_bs4$simulation$lf
tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio
ur_bs4 = Shock_bs4$simulation$ur
nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
s_h_bs4 = Shock_bs4$simulation$s_h
inflation_bs4 = Shock_bs4$simulation$inflation
y_bs4 = Shock_bs4$simulation$y
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
prod_ds_bs4 = Shock_bs4$simulation$prod_ds
prod_ds_shock_bs4 = Shock_bs4$simulation$prod_ds_shock
ur_bs4 = Shock_bs4$simulation$ur
pconk_ds_bs4 = Shock_bs4$simulation$pconk_ds
ik_bs4 = Shock_bs4$simulation$ik
gk_bs4 = Shock_bs4$simulation$gk
xk_ds_bs4 = Shock_bs4$simulation$xk_ds
mk_ds_bs4 = Shock_bs4$simulation$mk_ds

######### Hamid variable

AD_bs4= pconk_ds_bs4 + ik_bs4 + gk_bs4
TB_bs4= xk_ds_bs4 - mk_ds_bs4
```

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
yk_ds_01 = Shock_1$simulation$yk_ds
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_01 = Shock_1$simulation$yk
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
nben_h_un_01 = Shock_1$simulation$nben_h_un
lf_01 = Shock_1$simulation$lf
tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
s_g_01 = Shock_1$simulation$s_g
ur_01 = Shock_1$simulation$ur
nl_g_01 = Shock_1$simulation$nl_g
unemp_01 = Shock_1$simulation$unemp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
nben_g_01 = Shock_1$simulation$nben_g
yd_g_01 = Shock_1$simulation$yd_g
yh_g_01 = Shock_1$simulation$yh_g
tax_g_01 = Shock_1$simulation$tax_g
w_h_r_01 = Shock_1$simulation$w_h_r
tax_h_01 = Shock_1$simulation$tax_h
pconk_ds_01= Shock_1$simulation$pconk_ds
ik_01= Shock_1$simulation$ik
gk_01= Shock_1$simulation$gk
xk_ds_01= Shock_1$simulation$xk_ds
mk_ds_01= Shock_1$simulation$mk_ds

#### Hamid variable

AD_01= pconk_ds_01 + ik_01 + gk_01
TB_01= xk_ds_01 - mk_ds_01

@@

nben_h_un_02 = Shock_2$simulation$nben_h_un
yk_02 = Shock_2$simulation$yk
yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
ur_02 = Shock_2$simulation$ur
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02

#### Hamid variable

AD_02= pconk_ds_02 + ik_02 + gk_02
TB_02= xk_ds_02 - mk_ds_02

@@

```{r}
###Gengivelse af stød til model
max_dp_S1_base = sens_1_base_low$simulation$max_dp
wage_S1_base = sens_1_base_low$simulation$wage
komp_r_S1_base = sens_1_base_low$simulation$komp_r
part_S1_base = sens_1_base_low$simulation$part
yk_ds_S1_base = sens_1_base_low$simulation$yk_ds
pc_ds_S1_base = sens_1_base_low$simulation$pc_ds
unemp_S1_base = sens_1_base_low$simulation$unemp
dp_person_S1_base = sens_1_base_low$simulation$dp_person
nl_g_S1_base = sens_1_base_low$simulation$nl_g
yk_ds_S1_base= sens_1_base_low$simulation$yk_ds
pconk_ds_S1_base= sens_1_base_low$simulation$pconk_ds
ik_S1_base= sens_1_base_low$simulation$ik
gk_S1_base= sens_1_base_low$simulation$gk

xk_ds_S1_base= sens_1_base_low$simulation$xk_ds
mk_ds_S1_base= sens_1_base_low$simulation$mk_ds
ur_ds_S1_base= sens_1_base_low$simulation$ur_ds

#### Hamid variable

AD_S1_base= pconk_ds_S1_base + ik_S1_base + gk_S1_base
TB_S1_base= xk_ds_S1_base - mk_ds_S1_base
```

@@

shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)
